---
title: "Email Marketing at Capital OneITEC 621 - Homework 2 - Regression Refresher and Data Pre-Processing"
author: "Shawn Newman"
date: "Month dd, yyyy"
output: html_document
---

<span style="color:blue">*Note: save this file with the name HW1_YourLastName.Rmd [or HW2, etc.) and complete your homework in it.*</span>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
options(java.parameters = "-Xmx8g")
options("stringsAsFactors" = FALSE)
options(pillar.subtle_num = FALSE)
options(scipen=999)
library(dplyr)
library(mlr)
library(tidyr)
library(knitr)
library(fastDummies)
```


**1.1 Read in Data.** We began by reading in the data to R.

```{r}
data <- read.csv('C:/Users/shawn/Documents/KSB 620/FINAL2_SAMPLED100.TXT',
                 na.strings=c("NA","NaN", " ", ""))
```

**1.2 Remove missing data.** We next removed the variables where 99% of the data was the same.

```{r}
#---Remove variables with 99% missing (constant)--------------------------------
data.1 <- removeConstantFeatures(data, perc=0.01) #99% the same value

```

1.3 **SElect desired data** Next we selected the desired data fields that we will be working with.

```{r}
data.2 <- data.1 %>%
  select(RESP, days_since_last_activity, State, Upmarket, V42, V48, V88, V90, V140,V272,V274,V276,V278, MATCH)
```

1.4 **Impute missing data** We imputed the median Impute Missings w/Mean & Mode

```{r}
imp <- mlr::impute(data.2, classes = list(numeric=imputeMedian(),integer = imputeMedian()),
                   dummy.classes = c("character", "numeric", "integer"), dummy.type = "numeric") #You can include this or not

data.noMiss <- imp$data
```

1.5 **CReate Dummy Variables** YEs, there appears to be a gender pay gap with women earning less mean salary than men.

```{r}
#to_dummy <- c('V57', 'V90', 'V48', 'V41', 'V42', 'V138', 'V85', 'V47', 'V86', 'V160', 'V161', 'V159')
#to_dummy <- c('V3', 'V4', 'V7', 'V9', 'V10', 'V12', 'V13', 'V14', 'V15', 'V29', 'V30', 'V31', 'V32', 'V35', 'V36', 'V38', 'V40', 'V41', 'V42', 'V43')
to_dummy <- c('V140','V90','V88','V48','V42')

# convert to dummy variables and check the data
data_dummies <- fastDummies::dummy_cols(data.noMiss, select_columns = to_dummy)
head(data_dummies)
tail(data_dummies)

# get rid of the original columns that were made into dummy variables
list_to_keep <- setdiff(names(data_dummies), to_dummy)
data_dummies <- data_dummies[ , list_to_keep]

#Keep just numeric/integer
df<-data_dummies %>%
  select_if(is.numeric) %>%
  filter(MATCH == 1)
```

4. **lm() model, all variables **

```{r}

```

5. **lm() model, 5 variables **

```{r}
```

6. **Object's class**

```{r}
```

7. **What do these classes mean?**

```{r}
```

8. **Income.vect**

```{r}
```

9. **Mean, minimum, maximum, standard deviation and variance**

```{r}
```

10. **Income.stats** 

```{r}
```

11. **Vector Names**

```{r}
```

12. **5% Inflation**

```{r}
```

13. **Income Boxplot**

```{r}
```

14. **Income by Gender Boxplot**

```{r}
```

15. **Plot Credit Rating vs. Income**

```{r}
```

16. **Credit Rating Histogram**

```{r}
```

17. **Credit Rating qqplot** 

```{r}
```

18. **Is data normally distributed? Why or why not?**

```{r}
```

19. **ggplot2 Histogram**

```{r}
```

20. **Dual Line Plot**

```{r}
```
